%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------------------
  \cventry
 {National Institute of Aging, Data Tecnica International}
 {Biomedical Data Scientist}
 {Nov. 2021 - Present}
 {Bethesda, MD}
 	{
		\begin{cvitems}
		    \item {Improve and harmonize an scRNA-seq pipeline.}
		    \item {Collaborate with the iPSC Neurodegenerative Disease Initiative}
		    \item {Continued development on the GenoML automatic machine-learning pipeline}
        \end{cvitems}
 	}
 \cventry
 {National Institute of Child Health and Human Development, Bioinformatics and Scientific Programming Core}
 {Postbaccalaureate IRTA Fellow}
 {Jul. 2019 - May 2021}
 {Bethesda, MD}
 	{
		\begin{cvitems}
		    \item {Analyzed RNA-seq, proteomes, and structural biology data on an HPC file-system (Biowulf).}
		    \item {Wrote a tool to examine differential expression in Olink proteomic data, available at https://github.com/NICHD-BSPC/olink}
		    \item {Developed and tested various improvements to the bioinformatics workflows used by the group in R, Python, and Matlab using tools such as Snakemake, Gitlab CI and CircleCI.}
        	\item {Used continuous integration/continuous development frameworks to improve code quality and ensure long-term reproducibility of widely-used analysis code.}
        	\item {Performed primary and downstream analysis on high-throughput sequencing data, for example RNA-seq in a mouse model of the rare bone disease osteogenesis imperfecta, cell lines derived from patients with mutations in NPC1 causing a pediatric neurodegenerative disease, and a knockdown cell line derived from a pheochromocytoma patient, to understand how transcriptomes are perturbed in disease states.}
        \end{cvitems}
 	}
 \cventry
 {National Institute of Neurological Disorders and Stroke, Laboratory of Functional and Molecular Imaging}
 {Postbaccalaureate IRTA Fellow}
 {May 2018 - Jul. 2019}
 {Bethesda, MD}
 	{
		\begin{cvitems}
		    \item {Spearheaded the conversion to the Brain Imaging Data Structure (BIDS) data format to ease future data sharing.}
        	\item {Created a spellchecker for filtering search queries as well as a GUI for exoskeleton control in collaboration with another lab.}
        	\item {Coded a peripheral motion-tracker using openCV for analyzing sleep related motion, such as twitch, and a head-motion-independent alternative motion measure for motion-correction.}
        	\item {Assisted with preparing open-source polysomnography data by applying standard filters within EEGLAB (MATLAB package).}
        	\item {Utilized an open-source software suite (Analysis of Functional NeuroImages, a.k.a AFNI) consisting of C,Python,R,and shell scripts to differentiate high and low auditory arousal thresholds from sleep based on the temporal standard deviation of fMRI data.}
        %	\item {Ran analyses on an NIH-only HPC system (Biowulf), designed to support the NIH intramural research program, as part of a deep learning for image analysis course.}
        	\item {Collaborated with tech transfer personnel to obtain approval to ensure institutional polices were followed before disseminating intellectual property.}
        %	\item {Thoroughly researched the Brain Imaging Data Structure (BIDS) as a potential format for file naming for the purpose of sharing data.}
        	\item {Operated a Siemens Skyra VD13D commercial MRI platform to collect structural MRI images for clinical study.}
        %	\item {Unified a file-naming system for multiple data types (EEG, physiological, video, task-event-record files) for aligning runs associated with a sleep fMRI study.}
        %	\item {Assisted in drafting research publications.}
        \end{cvitems}
 	}
% {National Institute of Neurological Disorders and Stroke, Laboratory of Functional and Molecular Imaging}
 %{Postbaccalaureate IRTA Fellow}
% {May 2018 - June 2019}
% {Bethesda, MD}
% 	{
%		\begin{cvitems}
%        	\item {Collected, sorted and analyzed neuroimaging data.}
%        	\item {Coded a peripheral motion-tracker using openCV for analyzing sleep %related motion, such as twitch, and a head-motion-independent alternative motion measure %for motion-correction.}
%        	\item {Assisted in drafting research publications.}
%        \end{cvitems}
% 	}
 
 \cventry
    {Packaging Express, Inc.} % Organization
    {Data Support} % Job title
    {Nov. 2017 - April 2018} % Date(s)
    {Colorado Springs, CO} % Location
    {
     \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Automated the conversion of financial document images to spreadsheets.}
      \item {Mined a proprietary database for financial data to generate inventory reports.}
      \item {Performed standard accounting duties.}
     \end{cvitems}
   }

%---------------------------------------------------------
  \cventry
  	{Seagate Technology, LLC} % Organization
    {Software Engineer I} % Job title
    {Jul.-Sept. 2017} % Date(s)
    {Longmont, CO} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Eliminated external dependencies in proprietary code.}
        \item {Set up synchronized clusters using Puppet and proprietary technology.}
      \end{cvitems}
      %\begin{cvsubentries}
       % \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
        %\cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
%---------------------------------------------------------
  \cventry
  	{dpiX, LLC} % Organization
    {Yield Engineer Intern} % Job title
    {Apr.2014-Feb.2016;Aug.2016-Jan.2017} % Date(s)
    {Colorado Springs, CO} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented neural networks for image recognition.}
        \item {Wrote Python and VBA scripts for yield tabulation.}
        \item {Prepared scanning electron microscope samples.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
%---------------------------------------------------------
  \cventry
    {Center for Autism Research, Children’s Hospital of Philadelphia} % Organization
    {McMorris Fellow} % Job title
    {Jun. 2016 - Aug. 2016} % Date(s)
    {Philadelphia, PA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote Matlab scripts to synchronize wearable accelerometers.}
        \item {Recommended hardware and wearable devices for experiments.}
        \item {Assisted in designing and running experiments.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  	{Laboratory of Quantitative Neuromorphology, Dr. Bob Jacobs, The Colorado College} % Organization
    {Student Research Assistant} % Job title
    {Apr. 2012 - Aug. 2013} % Date(s)
    {Colorado Springs, CO} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepared figures for publication according to journal specifications.}
        \item {Pioneered the adoption of new lab software and procedures for its use.}
        \item {Authored step-by-step tracing and graphic-editing instructions for future assistants.}
      \end{cvitems}
    }
%\cventry
 % 	{CUTCO Cutlery, Vector Marketing} % Organization
  %  {Sales Representatives and Assistant Manager} % Job title
   % {Colorado Springs, CO} % Location
    %{Jun. 2010 - Aug. 2011} % Date(s)
    %{
     % \begin{cvitems} % Description(s) of tasks/responsibilities
      %  \item {Awarded the President's Award for selling \$13,000 worth of knives in one summer.}
       % \item {Coached other representatives over the phone.}
      %\end{cvitems}
    %}
%---------------------------------------------------------
\end{cventries}


