%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Relevant Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------------------
 \cventry
 {National Institute of Child Health and Human Development, Bioinformatics and Scientific Programming Core}
 {Postbaccalaureate IRTA Fellow}
 {July 2019 - Present}
 {Bethesda, MD}
 	{
		\begin{cvitems}
        	\item {Researched continuous integration/continuous development frameworks to improve code quality and ensure long-term reproducibility of widely-used analysis code.}
        	\item {Performed primary and downstream analysis on high-throughput sequencing data, for example RNA-seq in a mouse model of the rare bone disease osteogenesis imperfect, cell lines derived from patients with mutations in NPC1 causing a pediatric neurodegenerative disease, and a knockdown cell line derived froma pheochromocytoma patient, to understand how transcriptomes are perturbed in disease states.}
        	\item {Developed and tested various improvements to the bioinformatics workflows used by the group.}
        \end{cvitems}
 	}
 \cventry
 {National Institute of Neurological Disorders and Stroke, Laboratory of Functional and Molecular Imaging}
 {Postbaccalaureate IRTA Fellow}
 {May 2018 - Present}
 {Bethesda, MD}
 	{
		\begin{cvitems}
        	\item {Created a spellchecker for filtering search queries as well as a GUI for exoskeleton control in collaboration with another lab.}
        	\item {Coded a peripheral motion-tracker using openCV for analyzing sleep related motion, such as twitch, and a head-motion-independent alternative motion measure for motion-correction.}
        	\item {Assisted with preparing open-source polysomnography data by applying standard filters within EEGLAB (MATLAB package).}
        	%\item {Utilized an open-source software suite (Analysis of Functional NeuroImages, a.k.a AFNI) consisting of C, Python, R, and shell scripts to differentiate high and low auditory arousal thresholds from sleep based on the temporal standard deviation of fMRI data.}
        	\item {Ran analyses on an NIH-only HPC system (Biowulf), designed to support the NIH intramural research program, as part of a deep learning for image analysis course.}
        	\item {Collaborated with tech transfer personnel to obtain approval to ensure institutional polices were followed before disseminating intellectual property.}
        	%\item {Thoroughly researched the Brain Imaging Data Structure (BIDS) as a potential format for file naming for the purpose of sharing data.}
        	\item {Operated a Siemens Skyra VD13D commercial MRI platform to collect structural MRI images for clinical study.}
        	%\item {Unified a file-naming system for multiple data types (EEG, physiological, video, task-event-record files) for aligning runs associated with a sleep fMRI study.}
        	%\item {Assisted in drafting research publications.}
        \end{cvitems}
 	}

%---------------------------------------------------------
  \cventry
  	{Seagate Technology, LLC} % Organization
    {Software Engineer I} % Job title
    {Jul.-Sept. 2017} % Date(s)
    {Longmont, CO} % Location
    {
    %  \begin{cvitems} % Description(s) of tasks/responsibilities
    %    \item {Eliminated external dependencies in proprietary code.}
     %   \item {Set up synchronized clusters using Puppet and proprietary technology.}
     % \end{cvitems}
      %\begin{cvsubentries}
       % \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
        %\cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
%---------------------------------------------------------
  \cventry
  	{dpiX, LLC} % Organization
    {Yield Engineer Intern} % Job title
    {Apr.2014-Feb.2016;Aug.2016-Jan.2017} % Date(s)
    {Colorado Springs, CO} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented convolutional neural networks for classifying defects in the thin film transistors (TFTs).}
        \item {Co-authored a Python GUI and VBA scripts for yield tabulation.}
    \end{cvitems}
      %  \item {Prepared scanning electron microscope samples.}
     % \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
%---------------------------------------------------------
  \cventry
    {Center for Autism Research, Children’s Hospital of Philadelphia} % Organization
    {McMorris Fellow} % Job title
    {Jun. 2016 - Aug. 2016} % Date(s)
    {Philadelphia, PA} % Location
    {
    %  \begin{cvitems} % Description(s) of tasks/responsibilities
    %    \item {Wrote Matlab scripts to synchronize Empatica accelerometers.}
    %    \item {Recommended hardware and wearable devices for motion-capture and accelerometry experiments.}
    %    \item {Assisted in designing and running motion experiments in people with autism.}
    %  \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  	{Laboratory of Quantitative Neuromorphology, Dr. Bob Jacobs, The Colorado College} % Organization
    {Student Research Assistant} % Job title
    {Apr. 2012 - Aug. 2013} % Date(s)
    {Colorado Springs, CO} % Location
    {
     % \begin{cvitems} % Description(s) of tasks/responsibilities
     %   \item {Prepared figures for publication according to journal specifications.}
    %    \item {Pioneered the adoption of new lab software and procedures for its use.}
     %   \item {Authored step-by-step tracing and graphic-editing instructions for future assistants.}
     % \end{cvitems}
    }
%\cventry
 % 	{CUTCO Cutlery, Vector Marketing} % Organization
  %  {Sales Representatives and Assistant Manager} % Job title
   % {Colorado Springs, CO} % Location
    %{Jun. 2010 - Aug. 2011} % Date(s)
    %{
     % \begin{cvitems} % Description(s) of tasks/responsibilities
      %  \item {Awarded the President's Award for selling \$13,000 worth of knives in one summer.}
       % \item {Coached other representatives over the phone.}
      %\end{cvitems}
    %}
%---------------------------------------------------------
\end{cventries}
